Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-02-10 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Small tweaks

\begin{frame}
\frametitle{Heterogeneity in Business Practices}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2010, 2019): Business practices, motivation \citep{Bloom2010, Bloom2019}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Heterogeneity in Business Practices}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2010): Heterogeneity across mid-sized and large firms \citep{Bloom2010}
	\end{itemize_2pt}
\end{frame}

@@

Further specific channels of impact
\begin{enumerate_2pt}
	\item Better negotiation practices may affect raw material prices $\textcolor{red}{s}$
	\item Record-keeping and financial planning practices may affect borrowing constraints $\textcolor{red}{\lambda}$ through banks' willingness to lend
	\item Marketing practices may affect output price $\textcolor{red}{p}$ by changing demand

@@

\begin{frame}
\frametitle{Business Practices and Performance}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2019): Correlation with productivity across mid-sized and large firms \citep{Bloom2019}
	\item McKenzie2017: \textcolor{bdf}{Robust association with performance and firm survival} across industries and contexts in small firms
	\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Targeted Training}
	Female entrepreneurs
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Most common type of targeted training} (potentially complementary to classical microfinance model)
		\item Example: Gender and Enterprise Together \citep[GET Ahead, ILO;][]{Bulte2016,McKenziePuerto2020}
		\item ?
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

@@

%------------------------------------------------
\begin{frame}
\frametitle{A Growing Focus on Management}
\begin{itemize_2pt}
\item \textcolor{bdf}{Classroom Training}: Field, et al. (2010); Karlan \& Valdivia (2011); Bruhn \& Zia (2013); McKenzie \& Woodruff (2014, 2017); Bulte et al. (2017); Anderson, Chandy \& Zia (2018); Lafortune et al. (2018)
\vspace{0.1in}
\item \textcolor{bdf}{Consulting}: Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
\vspace{0.1in}

>>>>

\begin{frame}
\frametitle{Business Practices in Large Companies}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2010, 2019): Business practices, motivation \citep{Bloom2010, Bloom2019}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Business Practices in Large Companies}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2010): Heterogeneity across mid-sized and large firms \citep{Bloom2010, Bloom2016, Bloom2019}
	\end{itemize_2pt}
\end{frame}

@@

Further potential channels of impact
\begin{enumerate_2pt}
	\item Better negotiation practices may affect raw material prices $\textcolor{red}{s}$
	\item Record-keeping and financial planning practices may affect borrowing constraints $\textcolor{red}{\lambda}$ through banks' willingness to lend \citep[see, e.g.,][]{Bruhn2013} %Bruhn JDEff 2013 Stimulating managerial capital young entrepreneurs Bosnia
	\item Marketing practices may affect output price $\textcolor{red}{p}$ by changing demand

@@

\begin{frame}
\frametitle{Business Practices and Performance}
	\begin{itemize_2pt}
	\item Using panel data and a model that treats managerial capital as technology, \citet{Bloom2016} find differences in management practices account for about 30\% of cross-country TFP differences
	\item Bloom and van Reenen (2019): Correlation with productivity across mid-sized and large firms \citep{Bloom2019}
	\item McKenzie2017: \textcolor{bdf}{Robust association with performance and firm survival} across industries and contexts in small firms
	\end{itemize_2pt}

@@

\begin{frame}
\frametitle{Targeted Training}
	Female entrepreneurs
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Most common type of targeted training} (potentially complementary to classical microfinance model)
		\item Example: Gender and Enterprise Together \citep[GET Ahead, ILO;][]{Bulte2016,McKenziePuerto2020}
		\item ?
		\item More severe constraints, e.g., due to household-level reallocation \citep{Bernhardt2019, deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Sales vs. Profits}
Direct measurements
	\begin{itemize_2pt}
	\item \citep{Fafchamps2012} Personalized Digital Assistants (PDAs) for MSEs in Ghana
	\item[] $\rightarrow$ Vast majority of large changes in sales and profits genuine income volatility
	\end{itemize_2pt}
\end{frame}

@@

%------------------------------------------------
\begin{frame}
\frametitle{A Growing Focus on Management}
\begin{itemize_2pt}
\item \textcolor{bdf}{Classroom Training}: Field, et al. (2010); Karlan \& Valdivia (2011); Bruhn \& Zia (2013); McKenzie \& Woodruff (2014, 2017); Bulte et al. (2017); Anderson, Chandy \& Zia (2018); Lafortune et al. (2018)
\citep{Karlan2011}
\vspace{0.1in}
\item \textcolor{bdf}{Consulting}: Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
\vspace{0.1in}
